Bot's Guide to Being Human: Investigating the Effect of Conversation Architecture Elements on the Anthropomorphized Perceptions of Conversational Agents

### 2023-02-13 paper.tex
first draft complete! yay

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  TBD
\end{abstract}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{conversational agents, user perception, conversational architecture, social cues}

@@

\section{Introduction (Not Ready)}

@@

One of the key factors for anthropomorphized perception is how conversational agents convey information through verbal or non-verbal cues. Studies have found that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances, resulting in higher user satisfaction \cite{diederich2019emulating}\cite{yang2017perceived}. Also, CAs that mimic user behaviour through lexical alignment reduce users' cognitive workload, resulting in higher engagement with the interaction \cite{spillner2021talk}. Non-verbal cues such as expressive prosody contribute to higher perceived intimacy with the user, as well as higher perceived enjoyment and ease of use \cite{kim2020can}. However, conversational architecture design may lead to negative consequences, such as an agent with an extroverted personality may be seen as less trustworthy, as users are irritated by the system's overly familiar attitude \cite{andrews2012system}.

Even though there are existing research efforts investigating the effect of various conversational architecture elements on the anthropomorphized perception of agents, there is no clear view on the overall landscape on the state of research to understand what has been studied and what needs more efforts. Some reasons for this gap could be due to the lack of consistency in perception measures such as humanness or empathy. There are various questionnaires used in the studies (e.g. Godspeed Questionnaire) but their definitions for perceptions may be different. Also, there are various confounding factors like prior experience and domain of usage that makes it hard to generalize design principles for anthropomorphized perception of agents.

This paper attempts to address this gap in knowledge by investigating the following research questions: (RQ1) How does the specifics of conversational architecture design affect the anthropomorphized perception of CAs? and (RQ2) How does the specifics of conversational architecture design affect the perception of interaction with CAs? Through a comprehensive review of the existing literature, this paper presents the synthesis of a design framework developed based on X number of paper published between 2010 and 2022. The framework associated four categories of perception - interaction, ability of the agent, human attributes of the agent, and social connections with the user, with four categories of conversational architecture elements - verbal (content, style), visual (CMC), auditory (voice qualities, vocalizations), and chronemics adapted from Feine et al \cite{feine2019taxonomy}.

<One paragraph summarizing results>

<One paragraph outlining contributions to the HCI community>
* Synthesize existing framework into design framework \newline
* Point out gaps in research \newline

In the remainder of the paper, we first review the existing literature on design frameworks for conversational agents and measures of anthropomorphized perceptions. We then describe our literature review and data analysis process, following by describing the design framework synthesized based on findings of the collected literature corpus. Finally, we discuss the critical gaps in research identified through our analysis, and propose key opportunities for future research.

Design the conversational agents

@@

%Synthesis on conversational architecture

%Synthesis on measures

%Connections between conversational architecture elements and measures

@@

TBD

@@

\begin{tabular}{@{}p{3.1cm} | p{2cm} | p{4cm} | p{1.5cm} | p{6cm} @{}}

@@

\multirow{3}{*}{\parbox{3cm}{Perception of Interaction with Agent}}

@@

    & \cite{ashktorab2019resilient}\cmt{[88]}
    \cite{ceha2022expressive}\cmt{[77]}
    \cite{chan2021kinvoices}\cmt{[74]}
    \cite{choi2020nobody}\cmt{[54]}
    \cite{cuadra2021my}\cmt{[67]}
    \cite{dubiel2020persuasive}\cmt{[60]}
    \cite{elsholz2019exploring}\cmt{[61]}
    \cite{haas2022keep}\cmt{[78]}
    \cite{habler2019effects}\cmt{[63]}
    \cite{healey2013relating}\cmt{[39]}
    \cite{hu2022polite}\cmt{[76]}
    \cite{huiyang2022improving}\cmt{[17]}
    \cite{jestin2022effects}\cmt{[81]}
    \cite{kim2019comparing}\cmt{[89]}
    \cite{kim2020can}\cmt{[24]}
    \cite{kraus2020effects}\cmt{[64]}
    \cite{linnemann2018can}\cmt{[15]}
    \cite{ma2022ask}\cmt{[29]}
    \cite{miehle2018exploring}\cmt{[51]}
    \cite{misu2011toward}\cmt{[83]}
    \cite{roy2021users}\cmt{[71]}
    \cite{spillner2021talk}\cmt{[18]}
    \cite{wilhelm2022keep}\cmt{[28]}

@@

    & \cite{andrews2012system}\cmt{[38]}
    \cite{ceha2022expressive}\cmt{[77]}
    \cite{ceha2021can}\cmt{[57]}
    \cite{chan2021kinvoices}\cmt{[74]}
    \cite{cox2022does}\cmt{[27]}
    \cite{cuadra2021my}\cmt{[67]}
    \cite{elsholz2019exploring}\cmt{[61]}
    \cite{fadhil2018effect}\cmt{[52]}
    \cite{gnewuch2022opposing}\cmt{[20]}
    \cite{go2021conversational}\cmt{[80]}
    \cite{healey2013relating}\cmt{[39]}
    \cite{huiyang2022improving}\cmt{[17]}
    \cite{jestin2022effects}\cmt{[81]}
    \cite{kim2020can}\cmt{[24]}
    \cite{kim2019comparing}\cmt{[89]}
    \cite{lee2020hear}\cmt{[23]}
    \cite{linnemann2018can}\cmt{[15]}
    \cite{ma2022ask}\cmt{[29]}
    \cite{miehle2018exploring}\cmt{[51]}
    \cite{miyamoto2017improving}\cmt{[46]}
    \cite{moilanen2022measuring}\cmt{[82]}
    \cite{roy2021users}\cmt{[71]}
    \cite{spillner2021talk}\cmt{[18]}
    \cite{volkel2021examining}\cmt{[69]}
    \cite{volkel2022user}\cmt{[75]}
    \cite{xiao2021let}\cmt{[73]}
    \cite{yang2021effect}\cmt{[72]}
    \cite{zhu2022effects}\cmt{[26]}    

@@

    & \cite{ceha2022expressive}\cmt{[77]}
    \cite{choi2020nobody}\cmt{[54]}
    \cite{diederich2019emulating}\cmt{[25]}
    \cite{elsholz2019exploring}\cmt{[61]}
    \cite{habler2019effects}\cmt{[63]}
    \cite{gnewuch2018faster}\cmt{[19]}
    \cite{hoegen2019end}\cmt{[31]}
    \cite{hu2022polite}\cmt{[76]}
    \cite{ma2022ask}\cmt{[29]}
    \cite{roy2021users}\cmt{[71]}
    \cite{wilhelm2022keep}\cmt{[28]}
    \cite{yang2017perceived}\cmt{[44]}

@@

\multirow{3}{*}{\parbox{3cm}{Perception of Agent's Ability}}

@@

    & \cite{ashktorab2019resilient}\cmt{[88]}
    \cite{ceha2021can}\cmt{[57]}
    \cite{chan2021kinvoices}\cmt{[74]}
    \cite{cuadra2021my}\cmt{[67]}
    \cite{dubiel2020persuasive}\cmt{[60]}
    \cite{feijoo2021effects}\cmt{[70]}
    \cite{hu2021enhancing}\cmt{[56]}
    \cite{jeong2019exploring}\cmt{[10]}
    \cite{spillner2021talk}\cmt{[18]}
    \cite{volkel2022user}\cmt{[75]}
    \cite{yang2017perceived}\cmt{[44]} 

@@

    & \cite{cox2022does}\cmt{[27]}
    \cite{kraus2020effects}\cmt{[64]}
    \cite{lee2019s}\cmt{[55]}
    \cite{westerman2019believe}\cmt{[9]}

@@

    & \cite{andrews2012system}\cmt{[38]}
    \cite{chan2021kinvoices}\cmt{[74]}
    \cite{dubiel2020persuasive}\cmt{[60]}
    \cite{fadhil2018effect}\cmt{[52]}
    \cite{healey2013relating}\cmt{[39]}
    \cite{hoegen2019end}\cmt{[31]}
    \cite{huiyang2022improving}\cmt{[17]}
    \cite{jestin2022effects}\cmt{[81]}
    \cite{kraus2020effects}\cmt{[64]}
    \cite{lee2020hear}\cmt{[23]}
    \cite{linnemann2018can}\cmt{[15]}
    \cite{ma2022ask}\cmt{[29]}
    \cite{seeger2021chatbots}\cmt{[35]}
    \cite{tolmeijer2021female}\cmt{[62]}
    \cite{wilhelm2022keep}\cmt{[28]}    

@@

\multirow{3}{*}{\parbox{3cm}{Perception of Social Connection with Agent}}

@@

    & \cite{chan2021kinvoices}\cmt{[74]}
    \cite{cox2022does}\cmt{[27]}
    \cite{cuadra2021my}\cmt{[67]}
    \cite{daher2020empathic}\cmt{[58]}
    \cite{diederich2019emulating}\cmt{[25]}
    \cite{dubiel2020persuasive}\cmt{[60]}
    \cite{hu2021enhancing}\cmt{[56]}
    \cite{jestin2022effects}\cmt{[81]}
    \cite{misu2011toward}\cmt{[83]}
    \cite{tolmeijer2021female}\cmt{[62]}
    \cite{yang2021effect}\cmt{[72]}
    \cite{yang2017perceived}\cmt{[44]}
    \cite{zhu2022effects}\cmt{[26]}           

@@

    & Social Presence & connectedness, familiarity, similarity, psychological distance & 18
    & \cite{ceha2022expressive}\cmt{[77]}
    \cite{ceha2021can}\cmt{[57]}
    \cite{chan2021kinvoices}\cmt{[74]}
    \cite{choi2020nobody}\cmt{[54]}
    \cite{cuadra2021my}\cmt{[67]}
    \cite{diederich2019emulating}\cmt{[25]}
    \cite{gnewuch2018faster}\cmt{[19]}
    \cite{gnewuch2018chatbot}\cmt{[21]}
    \cite{gnewuch2022opposing}\cmt{[20]}
    \cite{go2021conversational}\cmt{[80]}
    \cite{khooshabeh2011does}\cmt{[37]}
    \cite{kim2020can}\cmt{[24]}
    \cite{lee2019s}\cmt{[55]}
    \cite{lubis2019positive}\cmt{[43]}
    \cite{lubold2016effects}\cmt{[86]}
    \cite{ma2022ask}\cmt{[29]}
    \cite{niewiadomski2013laugh}\cmt{[85]}
    \cite{westerman2019believe}\cmt{[9]}    

@@

    & \cite{choi2020nobody}\cmt{[54]}
    \cite{khooshabeh2011does}\cmt{[37]}
    \cite{kim2020can}\cmt{[24]}
    \cite{lee2020hear}\cmt{[23]}
    \cite{linnemann2018can}\cmt{[15]}
    \cite{lubold2016effects}\cmt{[86]}
    \cite{westerman2019believe}\cmt{[9]}

@@

\multirow{2}{*}{\parbox{3cm}{Perception of Agent's Humanness}}

@@

    & \cite{ashktorab2019resilient}\cmt{[88]}
    \cite{ceha2021can}\cmt{[57]}
    \cite{chan2021kinvoices}\cmt{[74]}
    \cite{choi2020nobody}\cmt{[54]}
    \cite{cox2022does}\cmt{[27]}
    \cite{diederich2019emulating}\cmt{[25]}
    \cite{gnewuch2018faster}\cmt{[19]}
    \cite{haas2022keep}\cmt{[78]}
    \cite{hu2022polite}\cmt{[76]}
    \cite{jeong2019exploring}\cmt{[10]}
    \cite{jestin2022effects}\cmt{[81]}
    \cite{lubis2019positive}\cmt{[43]}
    \cite{ma2022ask}\cmt{[29]}
    \cite{misu2011toward}\cmt{[83]}
    \cite{niewiadomski2013laugh}\cmt{[85]}
    \cite{ouchi2019should}\cmt{[59]}
    \cite{seeger2021chatbots}\cmt{[35]}
    \cite{wester2015artificial}\cmt{[14]}
    \cite{westerman2019believe}\cmt{[9]}
    \cite{zhu2022effects}\cmt{[26]}    

@@

    & \cite{andrews2012system}\cmt{[38]}
    \cite{ashktorab2019resilient}\cmt{[88]}
    \cite{ceha2022expressive}\cmt{[77]}
    \cite{ceha2021can}\cmt{[57]}
    \cite{chan2021kinvoices}\cmt{[74]}
    \cite{cox2022does}\cmt{[27]}
    \cite{cuadra2021my}\cmt{[67]}
    \cite{haas2022keep}\cmt{[78]}
    \cite{habler2019effects}\cmt{[63]}
    \cite{healey2013relating}\cmt{[39]}
    \cite{hu2022polite}\cmt{[76]}
    \cite{huiyang2022improving}\cmt{[17]}
    \cite{jeong2019exploring}\cmt{[10]}
    \cite{jestin2022effects}\cmt{[81]}
    \cite{khooshabeh2011does}\cmt{[37]}
    \cite{kim2019comparing}\cmt{[89]}
    \cite{lee2019s}\cmt{[55]}
    \cite{lee2020hear}\cmt{[23]}
    \cite{linnemann2018can}\cmt{[15]}
    \cite{miehle2018exploring}\cmt{[51]}
    \cite{moilanen2022measuring}\cmt{[82]}
    \cite{ouchi2019should}\cmt{[59]}
    \cite{tolmeijer2021female}\cmt{[62]}
    \cite{volkel2021manipulating}\cmt{[68]}
    \cite{volkel2022user}\cmt{[75]}
    \cite{wester2015artificial}\cmt{[14]}
    \cite{zhu2022effects}\cmt{[26]} 

@@

Modality?

\begin{table*}[h]
%\resizebox{\textwidth}{!}{
\begin{tabular}{@{}lllc@{}}
\toprule
 \textbf{Category} & \textbf{Theme}      & \textbf{Sample Codes}                                      & \textbf{No. Papers} \\ \midrule
\multirow{4}{*}{Linguistic Content}    & Affective Language & emotional expressions, sentiment-adaptive responses & 11 \\
 & Social Talk           & self-disclosure, social dialogue                       & 7                                       \\
 & Humour                & humorous content, jokes                                & 5                                       \\
 & Agent-Initiated Content & elicit user feedback, proactivity, conversation repair & 4                                       \\ \midrule
\multirow{4}{*}{Linguistic Style}     & Formality          & formal vs. casual, honorific expressions                               & 9  \\
 & Alignment             & content matching, lexical alignment, agreeableness     & 7                                       \\
 & Elaborateness         & elaborate, concise, sentence structure                 & 6                                       \\
 & Disfluency            & fillers, interjections, repetitions                    & 6                                       \\ \midrule
\multirow{2}{*}{Non-Linguistic Format}     & Prosodic Cue            & pitch, intonation, speech rate, spoken accent                          & 12 \\
 & Text Variation        & typo, capitalization, emoticons, response delay & 9                                         \\ \bottomrule 
\end{tabular}%
%}
\caption{Conversation architecture elements}
\label{tab:cues}
\end{table*}

@@

\subsubsection{Other Influencing Factors}

@@

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
The natural language interactions of conversational agents encourage users to attribute humanlike qualities to them, but we don't yet have a systematic understanding on how to design conversation architecture to orchestrate these anthropomorphized perceptions. Through a comprehensive review on papers with empirical studies on the impact of conversation architecture elements on perception of agents, we collected explored connections in literature to create a consistent taxonomy for anthropomorphized perceptions, and conversation architecture elements. Also, we created a generalized framework of the relationship between conversation architecture and perceptions based on the number of impacts found in the reviewed studies. In our analysis, we found there are inconsistencies in the measurements for perceptions of agents, as well as influencing factors other than conversation architecture that could impact anthropomorphized perceptions of agents. Also, it is important to consider ethical aspects of designing anthropomorphized perceptions of CAs as it may have negative consequences to users.
\end{abstract}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{conversational agents, user perception, conversational architecture, anthropomorphized perceptions, social cues}

@@

\section{Introduction}

@@

One of the key factors for anthropomorphized perception is how conversational agents convey information through verbal or non-verbal cues. Studies have found that conversational agents are perceived as more socially present and emotionally intelligent if they use affect language such as sentiment-adaptive response based on user's utterances, resulting in higher user satisfaction \cite{diederich2019emulating}\cite{yang2017perceived}. Also, CAs that mimic user behaviour through lexical alignment reduce users' cognitive workload, resulting in higher engagement with the interaction \cite{spillner2021talk}. Non-linguistic cues such as expressive prosody contribute to higher perceived intimacy with the user, as well as higher perceived enjoyment and ease of use \cite{kim2020can}. While there is existing research on the impact of conversation architecture on anthropomorphized perceptions of agents, their findings are hard to generalize due to obstacles in consistency of taxonomy and measures.
%However, conversational architecture design may lead to negative consequences, such as an agent with an extroverted personality may be seen as less trustworthy, as users are irritated by the system's overly familiar attitude \cite{andrews2012system}.

 There have been recent efforts to systematically analyze UX measurements used to evaluate conversational agents. In Clark et al's review for the state of speech interfaces, the authors created a list the different concepts used to measure disembodied voice-based agents such as user attitudes and task performance \cite{clark2019state}. Rapp et al. \cite{rapp2021human} analyzed literature related specifically to text-based CAs, where the themes emerged from their analysis has aspects related to the anthropomorphized perceptions, like humanness and emotional experience. Most recently, Zheng et al's literature review on the UX research of CAs \cite{zheng2022ux} categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence. Specifically to measures related to anthropomorphized perceptions, there is a gap of research to systematically analyze the different aspects of these perceptions, as well as a consistent taxonomy to refer to them. Similarly for conversation architecture elements, there is existing research to systematically analyze them, like Feine et al \cite{feine2019taxonomy}'s overall framework provides consistent categories for social cues. However, it is unknown which conversation architecture elements have impacts on the perceptions of agents. Lastly, while there are various studies investigating the effect of  conversational architecture elements on the anthropomorphized perception of agents, we did not find any systematic review and analysis to generalize the findings into a usable framework.

We are addressing this research gap by analyzing how to design conversation architecture in order to orchestrate anthropomorphized perceptions of conversational agents. First, we want to understand (RQ1) what aspects of anthropomorphized perceptions are being explored that are affected by conversation architecture. Conversation architecture has various aspects that affect a CA's utterances such as the use of humour, emoticons, or lexical alignment. This leads to our second research question: (RQ2) what are the elements of conversation architecture that are relevant to anthropomorphized perceptions? Lastly, we want to understand the impact of conversation architecture on perceptions of agent, which leads to our third research question: (RQ3) what are the relationships between the specifics of conversation architecture elements and the anthropomorphized perceptions of CAs?

To answer these questions, we need to synthesize existing literature by performing a comprehensive review from 2010 to 2022 on the impact of conversation architecture elements on anthropomorphized perceptions of CAs (n=57). We collected perceptions that are affected by conversation architecture and grouped them into four categories and eleven themes (Table \ref{tab:perceptions}). Similarly, we analyzed the conversation architecture elements explored in literature and grouped them into three categories and ten themes (Table \ref{tab:cues}). Lastly, we coded the explored connections between conversation architecture and perceptions and demonstrated the impacted relationship into a generalized framework (Figure \ref{fig:heatmap-impact}). Through our analysis, we also found that there are inconsistencies on how anthropomorphized perceptions are measured across studies, as well as influencing factors other than conversation architecture that may be impacting the perceptions of agents.

This work contributes to the HCI community by presenting an in-depth analysis on the impact of conversation architecture on anthropomorphized perceptions. We created a taxonomy for perceptions and conversation architecture elements to provide consistent terms that can be used in future research. Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a generalized framework outlining the relationships between conversation architecture and anthropomorphized perceptions. This framework provides the foundational knowledge to design conversation agents to solicit specific social responses from users.

In the remainder of the paper, we first outline our literature review and data analysis process, as well as the characteristics of the papers in our reviewed corpus. Following that, we describe in detail the taxonomy of anthropomorphized perceptions, taxonomy of conversation architecture element, as well as the framework on the relationships between perceptions and conversation architecture. Finally, we discuss the research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate anthropomorphized perceptions of conversational agents.

@@

@@

@@

\begin{tabular}{@{}p{0.17\textwidth} | p{0.12\textwidth} | p{0.20\textwidth} | >{\centering}p{0.09\textwidth} | p{0.42\textwidth} @{}}

@@

\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Interaction with Agent}}

@@

    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{kim2020can}\cmt{[24]}
    \cite{kraus2020effects}\cmt{[64]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{misu2011toward}\cmt{[83]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{wilhelm2022keep}\cmt{[28]}

@@

    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{elsholz2019exploring}\cmt{[61]}\cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{healey2013relating}\cmt{[39]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{kim2019comparing}\cmt{[89]}
    \cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{miyamoto2017improving}\cmt{[46]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2022user}\cmt{[75]}\cite{xiao2021let}\cmt{[73]}\cite{yang2021effect}\cmt{[72]}\cite{zhu2022effects}\cmt{[26]}    

@@

    & \cite{ceha2022expressive}\cmt{[77]}\cite{choi2020nobody}\cmt{[54]}\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{gnewuch2018faster}\cmt{[19]}\cite{hoegen2019end}\cmt{[31]}\cite{hu2022polite}\cmt{[76]}\cite{ma2022ask}\cmt{[29]}\cite{roy2021users}\cmt{[71]}\cite{wilhelm2022keep}\cmt{[28]}\cite{yang2017perceived}\cmt{[44]}

@@

\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Agent's Ability}}

@@

    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]} 

@@

    & \cite{cox2022does}\cmt{[27]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2019s}\cmt{[55]}\cite{westerman2019believe}\cmt{[9]}

@@

    & \cite{andrews2012system}\cmt{[38]}\cite{chan2021kinvoices}\cmt{[74]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{fadhil2018effect}\cmt{[52]}\cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{seeger2021chatbots}\cmt{[35]}\cite{tolmeijer2021female}\cmt{[62]}\cite{wilhelm2022keep}\cmt{[28]}    

@@

\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Social Connection with Agent}}

@@

    & \cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{hu2021enhancing}\cmt{[56]}\cite{jestin2022effects}\cmt{[81]}\cite{misu2011toward}\cmt{[83]}\cite{tolmeijer2021female}\cmt{[62]}\cite{yang2021effect}\cmt{[72]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}

@@

    & Social Presence & connectedness, familiarity, psychological distance & 18
    & \cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{lubold2016effects}\cmt{[86]}
    \cite{ma2022ask}\cmt{[29]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{westerman2019believe}\cmt{[9]}    

@@

    & \cite{choi2020nobody}\cmt{[54]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{lubold2016effects}\cmt{[86]}\cite{westerman2019believe}\cmt{[9]}

@@

\multirow{2}{*}{\parbox{0.16\textwidth}{Perception of Agent's Humanness}}

@@

    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cox2022does}\cmt{[27]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{haas2022keep}\cmt{[78]}\cite{hu2022polite}\cmt{[76]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{lubis2019positive}\cmt{[43]}\cite{ma2022ask}\cmt{[29]}\cite{misu2011toward}\cmt{[83]}\cite{niewiadomski2013laugh}\cmt{[85]}
    \cite{ouchi2019should}\cmt{[59]}\cite{seeger2021chatbots}\cmt{[35]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{zhu2022effects}\cmt{[26]}    

@@

    & \cite{andrews2012system}\cmt{[38]}\cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{khooshabeh2011does}\cmt{[37]}
    \cite{kim2019comparing}\cmt{[89]}\cite{lee2019s}\cmt{[55]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{tolmeijer2021female}\cmt{[62]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}\cite{wester2015artificial}\cmt{[14]}\cite{zhu2022effects}\cmt{[26]} 

@@

\begin{table*}[h]
\resizebox{\textwidth}{!}{
\renewcommand*{\arraystretch}{1.4}
\begin{tabular}{@{}p{0.17\textwidth} | p{0.14\textwidth} | p{0.25\textwidth} | >{\centering}p{0.09\textwidth} | p{0.34\textwidth} @{}}
\Xhline{1.2pt}
\textbf{Category} & \textbf{Theme} & \textbf{Sample Codes} & \textbf{No. Papers} & \textbf{Papers}
\\ \Xhline{1.2pt}
\multirow{4}{*}{Linguistic Content}    & Affective Language & emotional expressions, sentiment-adaptive responses & 11
& \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{moilanen2022measuring}\cmt{[82]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
\\ \cline{2-5}
& Social Talk & self-disclosure, social dialogue & 7
& \cite{andrews2012system}\cmt{[38]}\cite{lee2020hear}\cmt{[23]}\cite{lubold2016effects}\cmt{[86]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
\\ \cline{2-5}
& Humour & humorous content, jokes & 5
& \cite{ceha2021can}\cmt{[57]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{miyamoto2017improving}\cmt{[46]}\cite{volkel2021manipulating}\cmt{[68]}
\\ \cline{2-5}
& Agent-Initiated Content & proactive dialogue, conversation repair & 4
& \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}\cite{kraus2020effects}\cmt{[64]}\cite{xiao2021let}\cmt{[73]}
\\ \Xhline{1.2pt}
\multirow{4}{*}{Linguistic Style} & Formality & formal vs. casual, honorific expressions & 9
& \cite{cox2022does}\cmt{[27]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{ma2022ask}\cmt{[29]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{volkel2022user}\cmt{[75]}
\\ \cline{2-5}
& Alignment & content matching, lexical alignment, agreeableness & 7
& \cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2021manipulating}\cmt{[68]}
\\ \cline{2-5}
& Elaborateness & elaborate, concise, sentence structure & 6
& \cite{haas2022keep}\cmt{[78]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
\\ \cline{2-5}
& Disfluency & fillers, interjections, repetitions & 6
& \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{wester2015artificial}\cmt{[14]}\cite{yang2021effect}\cmt{[72]}
\\ \Xhline{1.2pt}
\multirow{2}{*}{Non-Linguistic Format} & Prosodic Cue & pitch, intonation, speech rate, spoken accent & 12
& \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{habler2019effects}\cmt{[63]}\cite{hu2021enhancing}\cmt{[56]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{lubold2016effects}\cmt{[86]}\cite{misu2011toward}\cmt{[83]}\cite{tolmeijer2021female}\cmt{[62]}\cite{zhu2022effects}\cmt{[26]}
\\ \cline{2-5}
& Text Variation & typo, capitalization, emoticons, response delay & 9
& \cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{kim2019comparing}\cmt{[89]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{westerman2019believe}\cmt{[9]}\cite{wilhelm2022keep}\cmt{[28]}
\\ \Xhline{1.2pt}
\end{tabular}%
}
\caption{Conversation architecture elements}
\label{tab:cues}
\end{table*}

@@

\subsubsection{Nuances in Influencing Factors}

@@

%Designing for personalities, not individual elements
